---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Percentage Difference Over Time (Walkthrough)

This document steps through the code to produce the figure in [README.md](./README.md). The output (.md/.html files) can be generated from the input (.Rmd files) using the following commands:

```{r example,eval=FALSE}
rmarkdown::render('./walkthrough.Rmd')
rmarkdown::render('./README.Rmd')
```

The first thing we need are some libraries to munge the data and create the graphic:

```{r setup}
## tidyverse brings in a bunch of useful packages
## here provides easy to use relative paths (to the .git folder)
## install.packages('tidyverse'); install.packages('here')
library(tidyverse)
library(here)
```

OK. Let's read in the data that Aaron's provided and take a quick look at it:

```{r read-in-data}
time_machine <- read_csv(here('datasets/vol1/resultsFromTheTimeMachine.csv'))
glimpse(time_machine)
```
