---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE
)
```

# Season-end Percentage (Walkthrough)

This document steps through the code to produce the figure in [README.md](./README.md). The output (.md/.html files) can be generated from the input (.Rmd files) using the following commands:

```{r example,eval=FALSE}
rmarkdown::render('./walkthrough.Rmd')
rmarkdown::render('./README.Rmd')
```

The first thing we need are some libraries to munge the data and create the graphic:

```{r setup}
## tidyverse brings in a bunch of useful packages
## here provides easy to use relative paths (to the .git folder)
## magick allows us to read in png
## install.packages('tidyverse'); install.packages('here')
## install.packages('magick')
library(tidyverse)
library(here)
library(magick)
```

OK. Let's read in the data that Aaron's provided and take a quick look at it:

```{r read-in-data}
time_machine <- read_csv(here('datasets/vol1/resultsFromTheTimeMachine.csv'))
glimpse(time_machine)
```

Looks like it's already 'tidy', so we should be able to get a very simple version of a graphic straight up. I'm going to look at season-end percentage, over time, so I'll first ensure everything's in the order I want. Here's the resulting simple figure:

```{r simple-figure}
time_machine <- time_machine %>%
  arrange(team, year)
time_machine %>%
  ggplot(aes(x = year, y = Gper, group = team)) +
  geom_point() +
  geom_path()

```

I don't like the points, so we'll get rid of those. I'm also going to pull out a couple of teams to highlight, keeping the rest of the teams in the 'background' by colouring them a light grey. We'll get rid of the background as well, maybe some other things after seeing what it looks like!

```{r highlight-teams}
## set up a colour vector
time_machine <- time_machine %>%
  mutate(
    colour = case_when(
      team == 'Fever' ~ '#05AE5F',
      team == 'Vixens' ~ '#DF005A',
      TRUE ~ 'lightgrey'
    )
  )
time_machine %>%
  ggplot(aes(x = year, y = Gper, group = team, colour = colour)) +
  geom_path() +
  scale_colour_identity() +
  theme_minimal()

```

That's not too bad, but let's add a little more bling. Aaron's added some logos, so we'll add those to call out the teams. We'll remove gridlines, they're not pleasant; add some nicer labelling, and also add a marker splitting the figure into ANZC vs SSN.

First, we'll read in the logos:

```{r logos}
vixens <- image_read(here('examples/vol1/images/Vixens_small.png')) %>%
  as.raster()
fever <- image_read(here('examples/vol1/images/Fever_small.png')) %>%
  as.raster()

```

Now we'll apply the logos at the appropriate positions, remove gridlines and add in the nicer labelling/markers:

```{r bling-it-up}
bling_it <- time_machine %>%
  ggplot(aes(x = year, y = Gper, group = team, colour = colour)) +
  geom_path() +
  scale_colour_identity() +
  theme_classic() +
  geom_vline(
    xintercept = 2016.5, colour = 'darkgreen', alpha = 0.5,
    lty = 3
  ) +
  labs(
    x = '', y = 'Percentage',
    caption =
  str_wrap('End of season percentage for all ANZC and SSN teams. To the left of the dotted line are season end percentages in the ANZC, to the right, SSN.',
  100)
  ) +
  annotation_raster(vixens, 2020.5, 2021.5, 83, 88) +
  annotation_raster(fever, 2020.5, 2021.5, 117, 122)
bling_it

```

Now we can save it (by default, `ggsave` saves the last image, and the aspect ratio is the golden ratio):

```{r save-image}
ggsave(
  here('examples/vol1-sl/fig.png'),
  width = 9, height = 18 / (1 + sqrt(5)), dpi = 'retina'
)

```
